CorReg: model-based pretreatment for regression with correlated variables. Application in steel industry

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@472 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
\title{CorReg: model based pretreatment for regression with correlated variables. Application in steel industry}

@@

\begin{document}
\maketitle
\bigskip
{\bf Abstract.} Linear regression generally suppose to have decorrelated covariates. This hypothesis is often irrealist with industrial datasets that contains many highly correlated covariates due to the process, physcial laws,  {\it etc}. The proposed generative model consists in explicit modeling of the correlations with a family of linear regressions between the covariates permitting to obtain by marginalization a parsimonious correlation-free regression model, easily understandable and compatible with variable selection methods. The structure of correlations is found with an MCMC algorithm. An R package (\textsc{CorReg}) available on the CRAN implements this new method which will be illustrated on both simulated datasets and real-life datasets from steel industry.
\smallskip

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
\title{CorReg: model-based pretreatment for regression with correlated variables. Application in steel industry}

@@

\begin{document}
\maketitle
\bigskip
{\bf Abstract.} Linear regression outcomes are known to be damaged by correlated covariates. However many modern datasets are expected to convey more and more highly correlated covariates. We propose to explicitly model the correlations by a family of linear regressions between the covariates. Marginalization allows then to obtain a parsimonious correlation-free regression model, easily understandable and from which it is then possible to perform standard linear estimation methods including variables selection procedures for instance. The structure of correlations is found with an MCMC algorithm. An R package (\textsc{CorReg}) available on the CRAN implements this new method which will be illustrated on both simulated datasets and real-life datasets from steel industry where correlated variables are frequent.
\smallskip
